Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-06-14 paper/ms.tex

\newcommand{\Nbody}{$N$-body}
\newcommand{\SMUGGLE}{SMUGGLE}
\newcommand{\Msun}{\ensuremath{M_{\odot}}}

@@

We have performed a simulation of a disk galaxy using the finite-volume
gravito-hydrodynamics code AREPO.\cite{2010MNRAS.401..791S} In AREPO, the
fluid is discretized as a moving Voronoi mesh. We use the additional physics
in the galaxy formation module Stars and MUltiphase Gas in GaLaxiEs (SMUGGLE)
\cite{2019MNRAS.489.4233M}. SMUGGLE is a comprehensive and self-consistent
galaxy formation model with a wide range of physical processes, including
radiative heating/cooling, star formation, and stellar feedback. More detailed
information on SMUGGLE is given in the Methods section. Our disk galaxy is a
modified version of the GALAKOS model\cite{2020ApJ...890..117D}, which
consists of a stellar disk, stellar bulge, and dark matter halo. After
$\sim2.5\,\textrm{Gyr}$ of evolution, the GALAKOS disk forms a bar consistent
with the Milky Way bar in terms of pattern speed and length
($\sim40\,\textrm{km}/\textrm{s}/\textrm{kpc}$ and $\sim4.5\,\textrm{kpc}$,
respectively). We modify this setup to include a gas phase, the details of
which are provided in the Methods section.

@@

\item[Code Availability] A public version of the AREPO code is available at
\url{https://arepo-code.org/}. An associated GitHub repository containing
analysis and plotting scripts will be made publicly available (currently
private). For the submission stage, we have included a tarball of this
repository.

@@

\noindent
{\bf SMUGGLE model}
\\
\noindent
We use the Stars and MUltiphase Gas in GaLaxiEs (SMUGGLE) model
\cite{2019MNRAS.489.4233M} implemented within the moving-mesh, finite-volume
hydrodynamics and gravity code AREPO \cite{2010MNRAS.401..791S}. The SMUGGLE model
additionally includes radiative heating and cooling, star
formation, and stellar feedback. Explicit gas cooling and heating of the
multi-phase interstellar medium is implemented, covering temperature ranges
between $10$ and $10^8\,\textrm{K}$.

>>>>

\newcommand{\Nbody}{$N$-body}
\newcommand{\SMUGGLE}{SMUGGLE}
\newcommand{\AREPO}{\textsc{AREPO}}
\newcommand{\Msun}{\ensuremath{M_{\odot}}}

@@

We have performed a simulation of a disk galaxy using the finite-volume
gravito-hydrodynamics code \AREPO{}.\cite{2010MNRAS.401..791S} In \AREPO{}, the
fluid is discretized as a moving Voronoi mesh. We use the additional physics
in the galaxy formation module Stars and MUltiphase Gas in GaLaxiEs (SMUGGLE)
\cite{2019MNRAS.489.4233M}. SMUGGLE is a comprehensive and self-consistent
galaxy formation model with a wide range of physical processes, including
radiative heating/cooling, star formation, and stellar feedback. More detailed
information on SMUGGLE is given in the Methods section. Our disk galaxy is a
modified version of the GALAKOS model\cite{2020ApJ...890..117D}, which
consists of a stellar disk, stellar bulge, and dark matter halo. After
$\sim2.5\,\textrm{Gyr}$ of evolution, the GALAKOS disk forms a bar consistent
with the Milky Way bar in terms of pattern speed and length
($\sim40\,\textrm{km}/\textrm{s}/\textrm{kpc}$ and $\sim4.5\,\textrm{kpc}$,
respectively). We modify this setup to include a gas phase, the details of
which are provided in the Methods section.

@@

\item[Code Availability] A public version of the \AREPO{} code is available at
\url{https://arepo-code.org/}. An associated GitHub repository containing
analysis and plotting scripts will be made publicly available (currently
private). For the submission stage, we have included a tarball of this
repository.

@@

\noindent
{\bf SMUGGLE model}
\\
\noindent
We use the Stars and MUltiphase Gas in GaLaxiEs (SMUGGLE) model
\cite{2019MNRAS.489.4233M} implemented within the moving-mesh, finite-volume
hydrodynamics and gravity code \AREPO{} \cite{2010MNRAS.401..791S}. The SMUGGLE model
additionally includes radiative heating and cooling, star
formation, and stellar feedback. Explicit gas cooling and heating of the
multi-phase interstellar medium is implemented, covering temperature ranges
between $10$ and $10^8\,\textrm{K}$.
